---
title: "lec_5_sampling_distribution_YingSong"
author: "Ying Song"
date: "2/19/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# On your own

# So far, we have only focused on estimating the mean living area in homes in Ames.
# Now you'll try to estimate the mean home price.
# .Take a random sample of size 50 from  price . Using this sample, what is your
#  best point estimate of the population mean?
```{r load the data}
download.file("http://www.openintro.org/stat/data/ames.RData", destfile = "ames.RData")
load("ames.RData")
head(ames)
names(ames)
dim(ames)


area <- ames$Gr.Liv.Area
price <- ames$SalePrice

```

```{r}

summary(price)
samp1 = sample(price, 50 )
mean(samp1)
# best guess is from sample mean : $180976
```

# .Since you have access to the population, simulate the sampling distribution 
# for $\bar{x}_{price}$ price (sampling mean of price ) by taking 5000 samples from
# the population of size 50 and computing 5000 sample means.
# Store these means in a vector called  sample_means50 . Plot the data,
# then describe the shape of this sampling distribution. 
# Based on this sampling distribution, what would you guess the mean home price of
# the population to be? Finally, calculate and report the population mean.
```{r for loop to get 5000 sample with sample size 50 }
sample_means50 <- rep(NA, 5000)
for (i in 1:5000){
  samp <- sample(price, 50)
  sample_means50[i] <- mean(samp)
}

hist(sample_means50, breaks = 25)

```

```

# .Change your sample size from 50 to 150, then compute the sampling distribution 
# using the same method as above, and store these means in a new vector called 
# sample_means150 . Describe the shape of this sampling distribution, and compare
# it to the sampling distribution for a sample size of 50.
# Based on this sampling distribution, what would you guess to be the mean sale
# price of homes in Ames?

# .Of the sampling distributions from 2 and 3, which has a smaller spread? 
# If we're concerned with making estimates that are more often close to the 
# true value, would we prefer a distribution with a large or small spread?


```{r }
sample_means150 <- rep(NA, 5000)
for (i in 1:5000){
  samp <- sample(price, 150)
  sample_means150[i] <- mean(samp)
}

par(mfrow = c(2,1))
xlimits <- range(sample_means50)
hist(sample_means50, breaks = 25, xlim = xlimits)
hist(sample_means150, breaks = 25, xlim = xlimits)

summary(sample_means150)
```

#The sampling distiribution with smaple size 150 has smaller spread, the better estimated mean is $180893. We prefer a distirubtion with smaller spread for estimation. 