---
title: " Solutions to Binomial and Poisson Practice Problems"
author: "Jiashu Song"
"
date: "`r Sys.Date()`"
output: html_document
---
The problems below will assist you in ensuring you have mastered finding probabilities from the Binomial and Poission distribution.

These problems are not being collected for a grade. Solutions will be posted by Wednesday May 20, 2020 so you may check your answers.

1. Use the appropriate R function (must be one we discussed from class) and find the following probabilities:

a. probability of 5 successes from a Bin(10,1/4) distribution. 

```{r}
dbinom(5,10,0.25)

```

b. probability of 5 or less successes from a Bin(10,1/4) distribution.


```{r}
pbinom(5,10,0.25,lower.tail=TRUE)
```

c. probability of less than 5 successes from a Bin(10,1/4) distribution.

```{r}
pbinom(4,10,0.25,lower.tail=TRUE)
```

d. probability of 5 or more successess from a Bin(10,1/4) distribution.

```{r}
1- pbinom(4,10,0.25,lower.tail=TRUE)

#OR

dbinom(5,10,0.25) + pbinom(5,10,0.25,lower.tail=FALSE)
```

e. probability of more than 5 successess from a Bin(10,1/4) distribution.

```{r}
pbinom(5,10,0.25,lower.tail=FALSE)
```


2. You are a data analyst working for an insurance company. You are interested in the number of claims that get submitted per day. X=# claims filed in one day.You know the mean number of claims filed per day is 15.  

Use the appropriate R function (must be one we discussed in class) to find the probabilities below.

a. What is the probability that more than 10 claims will filed in one day?


```{r}
ppois(10,15,lower.tail=FALSE)

```


b. What is the probability that 10 or more claims will be filed in one day?

```{r}
1-ppois(9,15,lower.tail=TRUE)
```

c. What is the probability that more than 7 claims will be filed in one day?

```{r}
ppois(7,15,lower.tail=FALSE)
```

d. What is the probability that 6 or less claims will be filed in one day?

```{r}
ppois(6,15,lower.tail=TRUE)
```


e. What is the probability that less than 6 claims will be filed in one day?

```{r}
ppois(5,15,lower.tail=TRUE)
```

f. What is the probability that exactly 7 claims will be filed in one day?

```{r}
dpois(7,15)
```







