---
title: "Binomial and Poisson Assignment"
author: "Jiashu Song"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

This assignment is worth 100 points. There are 12 questions and each question is worth 8 points each. 

Once you have all your code developed in each code chunk and/or typed your responses for the problems, knit the .Rmd file to an .HTML file. Save the .HTML file as 'Binomial_and_Poisson_yourlastname.HTML' and upload to the assignment link in Canvas.

Due Date: Thursday May 28, 2020 by 11:59p.m. EST. No late assignments accepted.


```{r}
library(vcd)
library(vcdExtra)

ds <- datasets(package = c("vcd", "vcdExtra"))
str(ds)
View(ds)
View(CyclingDeaths)
```

In the vcd package, there is a table entitled WomenQueue. Read the description of this data on p.p. 98-99 in the text. 

1. Is this scenario a binomial distribution? 
If yes, list the four properties that are satisfied and state n and p for this scenario.

If no, state which property is not satisfied.

ANS:
Yes! This scenario is a binomial distribution. 

It satifies the 4 properties:The WomenQueue data describes binary event ( female or male); 
Number of trails(n) is fixed, n =10 for this data.  
Each trail is independent.
The Pr(event) is constant value, for this case, p is 1/2. 

Therefore, we found: B(n,p) =  Bin(10, 0.5) 



2. In the WomenQueue table, what is the column that represents k and what is the column that represents $n_k$?

ANS:
nWomen represents K, and Freq represents N_k

3. If the data does satisfy the properties of a binomial distribution, find the probabilities using the correct R function.

The random variable would be X=number of women in a queue

a. Find the probability of exactly 6 women in a queue.

```{r}
data(WomenQueue, package="vcd")
View(WomenQueue)


barplot(WomenQueue, xlab = 'Num of female', ylab = 'Freq', col = 'lightblue',  cex.names = 0.8)
df <- as.data.frame(WomenQueue)
df


dbinom(6, 10, 0.5)
# probability of exactly 6 women in a queue is 20.5%


```

b. Find the probability of less than 6 women in a queue.

```{r}
pbinom(5,10,0.5,lower.tail=TRUE)
#the probability of less than 6 women in a queue is 62.3%
```

c. Find the probability of 6 or less women in a queue.

```{r}
pbinom(6,10,0.5,lower.tail=TRUE)

# the probability of 6 or less women in a queue is 82.8%
```

d. Find the probability of 6 or more women in a queue.

```{r}
pbinom(5,10,0.5,lower.tail=FALSE)
#another way
1- pbinom(5,10,0.5,lower.tail=TRUE) 
#the probability of 6 or more women in a queue is 37.7%
```

e. Find the probability of more than 6 women in a queue.

```{r}
pbinom(6,10,0.5,lower.tail=FALSE)
#the probability of more than 6 women in a queue is 17.2%.
```

4. This problem returns to the London cycling data that we discussed in class on May 13. Using the London cycling data that is described on p. 71, perform the following.

a. Create two columns in the form of two vectors that contain the values of k that range from 0 to 7 and the associated probabilities (as we did in class during the November 4 class). Using these probabilities, find the following.

X=number of cycling deaths

```{r}

#code from p. 71 that creates the frequency distribution & Barplot
data("CyclingDeaths", package="vcdExtra")
CyclingDeaths.tab <- table(CyclingDeaths$deaths)
CyclingDeaths.tab

View(CyclingDeaths)

barplot(CyclingDeaths.tab,
        xlab = "Num of deaths", ylab = "Num of fortnights",
        col = "pink", cex.lab = 1.5)

#check Poisson distribution

with(CyclingDeaths, c(mean = mean(deaths),
                      var = var(deaths),
                      ratio = mean(deaths)/var(deaths)))
```
Index of dispersion is closed to 1. confirm the poisson distribution.

```{r}
#creating two columns, k(events) and Prob (probability of events)

k <- 0:7  #creating the number of events
mean.deaths <- mean(CyclingDeaths$deaths) #get mean 

Pk <- dpois(k, mean.deaths) #first agrument is value of k,second argument is lambda 
cbind(k,Prob=round(Pk,7))   
```

b. Find the probability of more than 4 cycling deaths.

```{r}
1- ppois(3, mean.deaths, lower.tail=TRUE)
# the probability of more than 4 cycling deaths is 0.28%.
```

c. Find the probability of exactly 2 cycling deaths.
```{r}
dpois(2, mean.deaths)
#the probability of exactly 2 cycling deaths is 9.12%.
```

d. Find the probability of 4 or less cycling deaths.
```{r}
ppois(4, mean.deaths, lower.tail=TRUE)
#the probability of 4 or less cycling deaths is 0.9996938%.
```

e. Find the probabily of less than 4 cycling deaths.
```{r}
ppois(3, mean.deaths, lower.tail=TRUE)

#the probabily of less than 4 cycling deaths is 99.72%.
```
