---
title: 'Executive Session #1 Exercises'
author: "Jiashu Song"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

This assignment is worth 100 points. Each question is worth 7.5 points each.

Submission Instructions: save the .HTML file as 'Executive Session1Exercises_yourlastname.HTML' and upload the HTML file to the assignment entitled 'Executive Session #1 Exercises' on or before Saturday May 9, 2020 by 12:00p.m. (noon) EST. No late assignments are accepted.


packages <-c("AER", "ca", "car","colorspace", "corrplot", "countreg", "directlabels", "effects", "ggparallel", "ggplot2", "ggtern", "gmodels", "gnm", "gpairs", "heplots", "Lahman", "lattice", "lmtest", "logmult", "MASS", "mgcv", "nnet", "plyr", "pscl", "RColorBrewer", "reshape2", "rms","rsm", "sandwich", "splines", "vcd", "vcdExtra", "VGAM", "xtable") 
install.packages(packages)
```{r}

```

1. #2.1 p.p. 60-61


Run the code chunk below. 

```{r}
library(vcd)
library(grid)
library(gnm)
library(vcdExtra)

ds <- datasets(package = c("vcd", "vcdExtra"))
str(ds, vec.len=2)

View(ds)

View(UCBAdmissions)
str(UCBAdmissions)
```


a. How many data sets are there altogether? How many are there in each package? 

```{r}
nrow(ds)

table(ds$Package)
```

b. Make a tabular display of the frequencies by Package and class. 
```{r}

table(ds$Package, ds$class)
```


c. Choose one or two data sets from this list, and examine their help files (e.g., help(Arthritis) or ?Arthritis). You can use, e.g., example(Arthritis) to run the R code for a given example. 

```{r}
help("CoalMiners")
example(Arthritis)
```


2. p. 61 #2.3 

a. Find the total number of cases contained in this table.

```{r}
View(UCBAdmissions)
sum(UCBAdmissions)
```

b. For each department, find the total number of applicants.

```{r}
str(UCBAdmissions) # A table

margin.table(UCBAdmissions, 3) # dept col is 3rd col 

xtabs(Freq~Dept, data=UCBAdmissions) #another way to do it!
```

c. For each department, find the overall proportion of applicants who were admitted. 

```{r}
prop.table(UCBAdmissions, 3)

admin.df<- as.data.frame(UCBAdmissions)

admin.cont <- xtabs(Freq~Dept + Admit, data = admin.df)
admin.cont

#Proportion
prop.table(admin.cont, 1)

```

d. Construct a tabular display of department (rows) and gender (columns), showing the proportion of applicants in each cell who were admitted relative to the total applicants in that cell. 

```{r}

array<- t(prop.table(ftable(Dept~Admit+Gender, data = UCBAdmissions))[1:2,])
array
dimnames(array) <- list(c('A','B','C','D','E','F'), c('Male', 'Female'))
array


```

3. p. 61 #2.4 a, c, e


a. Find the total number of cases represented in this table. 

```{r}
View(DanishWelfare)
help("DanishWelfare")
str(DanishWelfare)

sum(DanishWelfare$Freq)
```


c. Convert this data frame to table form, DanishWelfare.tab, a 4-way array containing the frequencies with appropriate variable names and level names. 

```{r}
#contingency table 

arrayD<-t(prop.table(ftable(Freq~Alcohol+ Income+ Status+ Urban, data = DanishWelfare))[2:5,])
dimnames(arrayD) <- list(c('A','B','C','D','E','F'), c('Male', 'Female'))
array

DanishWelfare.tab <- xtabs(Freq ~., data = DanishWelfare)
DanishWelfare.tab

```


e. Use structable () or ftable () to produce a pleasing flattened display of the frequencies in the 4-way table. Choose the variables used as row and column variables to make it easier to compare levels of Alcohol across the other factors. 

```{r}
ftable(DanishWelfare.tab)

```

4. p. 62 #2.5 a, b, c

```{r}
#code from text
data("UKSoccer", package = "vcd") # specify data from pacakge
ftable(UKSoccer)

help("UKSoccer")
```

a. a. Verify that the total number of games represented in this table is 380. 

```{r}
sum(UKSoccer)

```


b. Find the marginal total of the number of goals scored by each of the home and away teams. 

```{r}
margin.table(UKSoccer, 1) #Home
margin.table(UKSoccer, 2) # Away


```

c. Express each of the marginal totals as proportions. 

```{r}
# apply prop.table to marginal.table generated i question b. 
prop.table(margin.table(UKSoccer, 1)) 

prop.table(margin.table(UKSoccer, 2))

```

