---
title: "analytics500-midterm-q26"
author: "Jiashu Song"
date: "2/22/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Create a bar graph using the attached Iris dataset: iris_exams.csv
Preview the document (click to download). Compare the Sepal Length of the flower Species. Include the following:

Main Title
X and Y-Axis Labels
 Colors by Species 
Provide an interpretation in one paragraph  (no more than 300 words) explaining the distribution of the data. 
Which Species Sepal.Length is greater?


```{r }


df= read.csv('iris_exams.csv', header = TRUE)

summary(df)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
library(ggplot2)
# Sepal width
SL = df$Sepal.Length
ggplot(data=df, aes(x=SL))+
  geom_histogram(binwidth=0.2, color="white", aes(fill=Species)) + 
  xlab("Sepal Width (cm)")+
  ylab( "Frequency" )+
  ggtitle("Histogram of Sepal Width")+
  geom_vline(data=df, aes(xintercept = mean(SL)),linetype="dashed",color="black")


```
answer: from the plot above , we can tell the three distributions and mean. virginica with blue colar shows greater Sepal Width than the other two species. 

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
