---
title: "analytics500_midterm_code"
author: "Jiashu Song"
date: "2/22/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

1) Understanding the Data:

The structure of the data and a preview of the data.
Frequency Distribution. (Frequency Tables & Plots for each variable in the dataset (Barplots/Histograms)). Make sure to capture the skewness and kurtosis. - Provide an interpretation in one paragraph  (no more than 300 words) explaining the distribution of the data. 
Summary Statistics of the Data at least including mean, quartiles, min/max, and standard deviation. 

```{r iris}
library(moments)
library(plyr)

df = read.csv('iris_exams.csv', header = TRUE)
ls(df)
head(df)
```

##plot

```{r }
par(mfrow = c(2,2))
hist(df$Petal.Length,breaks = 25, xlab ='Petal Length')
hist(df$Petal.Width, breaks = 25, xlab ='Petal Width')
hist(df$Sepal.Length,breaks = 25, xlab ='Sepal Length')
hist(df$Sepal.Width, breaks = 50, xlab ='Sepal Width')
mean(df$Sepal.Width)
skewness(df$Sepal.Width)
kurtosis(df$Sepal.Width)
levels(df$Species)

#df_setosa = subset(data_iris, data_iris$Species == 'setosa')
#hist(df_setosa$Petal.Length)

```
answer: use the sepal width plot as example, the distribution shows slight positively skewness( 0.5065), kurtosisi is larger than 3 ( 3.2987). This histgram includes all three species sepal width distributions. Could dig more with group barplot with colored speices for further analysis. 

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
summary(df)

```

