---
title: "ANLY500_Final_Q3_YingSong"
author: "Jiashu Song"
date: "4/26/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Perform data screening making sure to check for accuracy, missing, outliers.
Perform assumption checks for linearity, normality, homogeneity, and homoscedasticity.
Capture a Correlation Matrix and Visual to express the relationship between each of the variables in the iris dataset.  
What is the correlated effect? Provide an interpretation in your own words. Support your response with results captured from the correlation analysis.  
Calculate the Variance. What does it tell us?
Calculate the Covariance. What does it tell us?

```{r load data}
data = read.csv("iris_exams.csv", header = TRUE)
```

Data screening: 

```{r data screeening}
## Accuracy check and Missing data check
summary(data)
## No data errors. No missing data.

## Outliers check using mahal cutoff 
str(data)

mahal = mahalanobis(data[,-c(1,2)],
                    colMeans(data[,-c(1,2)], na.rm = TRUE),
                    cov(data[,-c(1,2)], use = "pairwise.complete.obs"))
summary(mahal)

cutoff = qchisq(1-.001, ncol(data[,-c(1,2)]))
print(cutoff) # Mahal score


badmahal = as.numeric(mahal > cutoff) 
table(badmahal)
## 2 outliers are found.

## remove outliers
data_noout = subset(data, mahal < cutoff)
str(data_noout)
```

```{r generate the correlation matrix}
cor(data_noout$Petal.Length, data_noout$Petal.Width)

res <- cor(data_noout[,-c(1,2)])
round(res, 2)

```

```{r Correlation Matrix and Visual}
library("Hmisc")
res2 <- rcorr(as.matrix(data_noout[,-c(1,2)]))
res2

library(corrplot)
corrplot(cor(data_noout[,-c(1,2)]))

```
# calculate the variance:

```{r Variance.}
library(datasets)
cov(data_noout$Sepal.Length, data_noout$Sepal.Width)

cov = cov(data_noout[,-c(1,2)])
cov
#install.packages('plot.matrix')
library('plot.matrix')
library('psych')
fa <- fa(cov, 4, rotate="varimax")
par(mar=c(5.1, 4.1, 4.1, 4.1)) # adapt margins
plot(loadings(fa), cex=0.5)

```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
