---
title: "ANLY 500 Final exam -Q1"
author: "Jiashu Song"
date: "4/19/2020"
output:
  word_document: default
  html_document: default
---

	Capture a  Regression Model with Only Significant Variables.  
Set the dependent variable to 'Species'. 

	Capture the final model summary. Provide any visuals that help interpret the results. 
	Provide an interpretation of the results in your own words.  Support your response with results captured from the linear regression analysis.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r  Load data}
data <- read.csv("iris_exams.csv", header = TRUE)
head(data[2])

head(data[,-c(1,2)])
```

```{r  Data Screening}

## Accuracy check and Missing data check
summary(data)
## No data errors. No missing data.

## Outliers check using mahal cutoff 
str(data)

mahal = mahalanobis(data[,-c(1,2)],
                    colMeans(data[,-c(1,2)], na.rm = TRUE),
                    cov(data[,-c(1,2)], use = "pairwise.complete.obs"))
summary(mahal)

cutoff = qchisq(1-.001, ncol(data[,-c(1,2)]))
print(cutoff) # Mahal score


badmahal = as.numeric(mahal > cutoff) 
table(badmahal)
## 2 outliers are found.

## remove outliers
data_noout = subset(data, mahal < cutoff)
str(data_noout)



```

```{r assumption}

## Linearity
random = rchisq(nrow(data_noout[,-c(1,2)]),7)
fake = lm(random~., data = data_noout[,-c(1,2)])
summary(fake)

standardized = rstudent(fake)
qqnorm(standardized)
abline(0,1)
## Meet linearity

## Normality
hist(standardized, breaks = 15)
## slightly positive right skewness, meet normality.

## Homogeneity/Homoscedasticity
fitted = scale(fake$fitted.values)
plot(fitted, standardized)
abline(0,0)
abline(v = 0)
##  meet the homogenity and homoscedasticity.

```

```{r}
## Correlation Matrix and Visual
library(datasets)
cor(data_noout[,-c(1,2)])

library(corrplot)
corrplot(cor(data_noout[,-c(1,2)]))
```

    From the correlation matrix,  sepal length has strong postive correlation with petal length and petal width, and a weak negtive correlation with sepal width. Sepal width has strong negtive correlation with petal length and petal width. Petal length has a positive correlation with petal width.

```{r}
## Support the correlation analysis
library(ggplot2)
cleanup = theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 15))

## Sepal length & petal length
scatter1 = ggplot(data_noout, aes(Sepal.Length, Petal.Length))
scatter1 +
  geom_point() +
  geom_smooth(method = "lm", formula =y ~ x ) +
  xlab("Sepal Length") +
  ylab("Petal Length") +
  cleanup

## Sepal length & petal width
scatter2 = ggplot(data_noout, aes(Sepal.Length, Petal.Width))
scatter2 +
  geom_point() +
  geom_smooth(method = "lm", formula =y ~ x) +
  xlab("Sepal Length") +
  ylab("Petal Width") +
  cleanup

## Sepal length & sepal width
scatter3 = ggplot(data_noout, aes(Sepal.Length, Sepal.Width))
scatter3 +
  geom_point() +
  geom_smooth(method = "lm", formula =y ~ x) +
  xlab("Sepal Length") +
  ylab("Sepal Width") +
  cleanup

## Sepal width & petal length
scatter4 = ggplot(data_noout, aes(Sepal.Width, Petal.Length))
scatter4 +
  geom_point() +
  geom_smooth(method = "lm", formula =y ~ x) +
  xlab("Sepal Width") +
  ylab("Petal Length") +
  cleanup

## Sepal width & petal width
scatter5 = ggplot(data_noout, aes(Sepal.Width, Petal.Width))
scatter5 +
  geom_point() +
  geom_smooth(method = "lm", formula =y ~ x) +
  xlab("Sepal Width") +
  ylab("Petal Width") +
  cleanup

## Petal length & petal width
scatter6 = ggplot(data_noout, aes(Petal.Length, Petal.Width))
scatter6 +
  geom_point() +
  geom_smooth(method = "lm", formula =y ~ x) +
  xlab("Petal Length") +
  ylab("Petal Width") +
  cleanup
```

```{r}
## Variance and Covariance
var(data_noout[,-c(1,2)])

cov(data_noout[,-c(1,2)])

```

